% vim: ft=tex:
\documentclass[web-recipes.tex]{subfiles}
\begin{document}

\renewcommand{\mytitle}{American Chili Powder (Amazing Ribs)}
\renewcommand{\myurl}{https://amazingribs.com/tested-recipes/spice-rubs-and-pastes/homemade-american-chili-powder-recipe/}

\sbox{\ingredients}{%
  \begin{minipage}[t]{0.35\textwidth}
    {\sffamily\bfseries Ingredients}\vspace{0.5ex}
    \begin{itemize}
      \item 2 \nicefrac{1}{2} tablespoons ancho chile powder
      \item 1 teaspoon pasilla chile powder
      \item 1 teaspoon guajillo chile powder
      \item 1 teaspoon sweet American, Hungarian, or Spanish paprika
      \item 1 teaspoon dried oregano, crumbled
      \item 1 teaspoon ground black pepper
      \item \nicefrac{1}{2} teaspoon garlic powder
      \item \nicefrac{1}{2} teaspoon onion powder
      \item \nicefrac{1}{4} teaspoon cumin powder
    \end{itemize}
  \end{minipage}
}

\sbox{\method}{%
  \begin{minipage}[t]{0.55\textwidth}
    {\sffamily\bfseries Method}\vspace{0.5ex}
    \begin{enumerate}
      \item Prep. If possible start with whole dried chiles and make powders from them. Cut off the
        tops of the chiles with scissors and shake out the seeds. Poke around in the chile with a
        knife to get the rest. With the scissors cut the chiles lengthwise into two halves, and then
        into chunks about 1 inch (25 mm) square.
      \item Toast. Put the chunks into a medium hot frying pan for about 2 minutes, no oil, then
        shake the pan to flip as many as possible and toast them for another 2 minutes. This brings
        out the flavorful oils, a process called blooming.
      \item Powder. Grind the toasted chunks in a spice grinder, coffee grinder, blender, or food
        processor.
      \item Pour all the powdered ingredients in a bowl or jar and stir them all together.
      \item Use. The blend will still be useable for about a year, but the freshness and potency
        slowly declines.
    \end{enumerate}
  \end{minipage}
}

\sbox{\notes}{%
  \begin{minipage}[t]{0.6\textwidth}
    {\sffamily\bfseries Notes}\vspace{0.5ex}

    \begin{tabular}{lll}
      \textbf{Pepper} & \textbf{Weight} & \textbf{Volume} \\
      1 ancho & \nicefrac{1}{4} oz & 1 tbsp + 1 tsp \\
      1 pasilla &\nicefrac{1}{4} oz  & 1 tbsp + 1 tsp \\
      1 guajillo &\nicefrac{1}{8} oz  & 2 tsp \\
      1 chipotle &\nicefrac{1}{8} oz  & 2 tsp \\
    \end{tabular}
  \end{minipage}
}

\begin{mdframed}[nobreak]
  \section{\mytitle}
  \begin{tabular}{l}
    \usebox{\ingredients}\quad\usebox{\method}\vspace{3ex}\\
    \multicolumn{1}{l}{\usebox{\notes}}\vspace{3ex}\\
    \multicolumn{1}{c}{\small\ttfamily \url{\myurl}} \\
  \end{tabular}

\end{mdframed}
\end{document}
