% vim: ft=tex:
\documentclass[web-recipes.tex]{subfiles}
\begin{document}

\pagestyle{empty}

\renewcommand{\mytitle}{Spicy Chicken Quesadillas (Domesticate Me)}
\renewcommand{\myurl}{https://domesticate-me.com/spicy-chicken-quesadillas-corn-black-beans-caramelized-onions/}

\myRecipe{Mains}{\mytitle{}}

\sbox{\ingredients}{%
  \begin{minipage}[t]{\the\dimexpr 0.35\linewidth - 1em\relax}
    {\sffamily\bfseries Ingredients}\vspace{0.5ex}
    \begin{itemize}
      \item 1 tablespoon plus 1 teaspoon extra virgin olive oil divided
      \item 1 small red onion thinly sliced
      \item Kosher salt
      \item White pepper
      \item 1 ear yellow corn shucked
      \item 1 boneless skinless chicken breast or two thin-sliced chicken cutlets
      \item ¼ teaspoon smoked paprika
      \item 2 cups grated pepper jack cheese
      \item ½ cup canned black beans drained and rinsed
      \item 2 scallions white and light green parts only, thinly sliced
      \item 2 large 10-12 inch whole grain tortillas
      \item \textbf{optional}
        \begin{itemize}
          \item Salsa of your choice
          \item Guacamole
        \end{itemize}
    \end{itemize}
  \end{minipage}
}

\sbox{\method}{%
  \begin{minipage}[t]{\the\dimexpr 0.6\linewidth - 1em\relax}
    {\sffamily\bfseries Method}\vspace{0.5ex}
    \begin{enumerate}
      \item Heat a tablespoon of olive oil in a medium saucepan over medium heat. When hot, add the
        sliced red onions and a pinch of kosher salt and white pepper. Cook for about 10 minutes,
        stirring regularly, until the onions are soft and translucent. Remove from the pan and set
        aside.
      \item Use a sharp knife to remove the kernels from your shucked ear of corn.
      \item In the same pan you used for the onions, heat the remaining teaspoon of oil over medium
        heat. When hot, add the corn and a pinch of salt and white pepper. Cook, stirring
        periodically, for about 6 minutes until the corn is tender and lightly browned. Remove from
        the pan and set aside.
      \item Moving on to the chicken! Use a sharp knife to butterfly your chicken breast. Relax,
        it’s not that hard. Just place the breast on a cutting board, and carefully slice the breast
        in half widthwise almost to the other edge. Keep that edge intact and then open the breast
        along the fold. Season both sides of the chicken with the smoked paprika and a pinch of
        kosher salt.
      \item Heat a lightly oiled grill or grill pan (yes, you can use a regular pan if you must)
        over medium-high heat. When hot, add the chicken breast. Cook for 3-4 minutes on each side
        until the chicken is opaque and cooked through. Remove the chicken from the grill and let it
        cool slightly before slicing it into ½-inch cubes.
      \item Now it’s time to assemble your quesadillas. Sprinkle ½ cup cheese on one side of each
        tortilla.Top with half the caramelized onions, corn, cubed chicken, beans and scallions in
        an even layer. Sprinkle with another ½ cup cheese, and fold the other half of each tortilla
        over the toppings.
      \item Heat a large skillet or pan over medium heat. When hot, carefully add the quesadillas to
        the pan. Cook for 2-3 minutes on each side until the quesadillas are lightly browned and the
        cheese has melted.
      \item Carefully transfer the quesadillas to a cutting board and let them cool for a couple
        minutes before slicing each one into fourths. Serve with Guacamole and Salsa for even more
        awesomeness.
    \end{enumerate}
  \end{minipage}
}


  \begin{tabular}{l}
    \usebox{\ingredients}\hspace{1em}\usebox{\method}\vspace{3ex}\\
    \multicolumn{1}{c}{\small\ttfamily \url{\myurl}} \\
  \end{tabular}

\end{document}
