% vim: ft=tex:
\documentclass[web-recipes.tex]{subfiles}
\begin{document}

\pagestyle{empty}

\renewcommand{\mytitle}{Caramel Apple Turnovers (Food Thinkers)}
\renewcommand{\myurl}{https://www.foodthinkers.com/caramel-apple-turnovers/}

\sbox{\ingredients}{%
  \begin{minipage}[t]{0.35\textwidth}
    {\sffamily\bfseries Ingredients}\vspace{0.5ex}
    \begin{description}
      \item[For filling]\hfill
        \begin{itemize}
          \item 2 medium Granny Smith apples, peeled and diced (about 3 cups)
          \item 3 tablespoons unsalted butter
          \item \nicefrac{1}{2} cup dark brown sugar
          \item 1 teaspoon vanilla extract
          \item 1 teaspoon lemon juice
          \item \nicefrac{3}{4} teaspoon ground cinnamon
          \item \nicefrac{1}{4} teaspoon kosher salt
        \end{itemize}
      \item[For turnovers]\hfill
        \begin{itemize}
          \item 2 sheets frozen puff pastry (17 ounce package), thawed (keep cold until use)
          \item 1 egg
          \item 1 tablespoon water
          \item Turbinado sugar for sprinkling
        \end{itemize}
    \end{description}
  \end{minipage}
}

\sbox{\method}{%
  \begin{minipage}[t]{0.55\textwidth}
    {\sffamily\bfseries Method}\vspace{0.5ex}
    \begin{enumerate}
      \item Combine filling ingredients in a medium saucepan and cook over medium heat, stirring
        occasionally, until apples are tender and syrup is thick, about 10 minutes.
      \item Transfer apple mixture to a plate and chill in the refrigerator until cool to the touch,
        20-30 minutes.
      \item Scramble egg and water in a small bowl.
      \item Place 1 sheet of puff pastry on a clean cutting board; reserve second sheet in the
        refrigerator.
      \item Divide pastry into 4 equal squares. Spoon 2 tablespoons apple mixture onto the center of
        each square.
      \item Brush the edges of each square with egg wash. Fold pastry diagonally over apple mixture
        and seal the edges with a fork.
      \item Place turnovers on a plate and refrigerate while preparing remaining turnovers. Repeat
        steps 4-6 with second sheet of puff pastry.
      \item Select AIRFRY/325°F/SUPER CONVECTION/20 minutes and press START to preheat oven.
      \item Place turnovers on airfry rack. Brush tops with egg wash and sprinkle with turbinado
        sugar. Make 3 small slits in each turnover.
      \item Cook in rack position 4 until puffed and golden brown, about 20 minutes. Serve warm or
        at room temperature.
    \end{enumerate}
  \end{minipage}
}

\myRecipe{Desserts}{\mytitle{}}

% \addcontentsline{toc}{subsubsection}{\mytitle}
%   \subsubsection*{\mytitle}
  \begin{tabular}{l}
    \usebox{\ingredients}\qquad\usebox{\method}\vspace{3ex}\\
    \multicolumn{1}{c}{\small\ttfamily \url{\myurl}} \\
  \end{tabular}
\end{document}
