% vim: ft=tex:
\documentclass[web-recipes.tex]{subfiles}
\begin{document}

\pagestyle{empty}

\renewcommand{\mytitle}{Loaded Potato Bites (Food Thinkers)}
\renewcommand{\myurl}{https://www.foodthinkers.com/air-fry-recipes-loaded-potato-bites/}

\sbox{\ingredients}{%
  \begin{minipage}[t]{0.32\textwidth}
    {\sffamily\bfseries Ingredients}\vspace{0.5ex}
    \begin{itemize}
      \item 2 large russet potatoes (about 1\nicefrac{1}{2} pounds)
      \item \nicefrac{1}{4} cup sour cream + \nicefrac{1}{4} cup for dipping
      \item 1 egg
      \item \nicefrac{1}{4} cup (1 ounce) shredded cheddar cheese
      \item 4 slices bacon, cooked and finely chopped
      \item 2 tablespoons chopped chives
      \item 2 teaspoons kosher salt
      \item \nicefrac{1}{2} teaspoon freshly ground black pepper
      \item {\bfseries To bread}
        \begin{itemize}
          \item 1 egg
          \item 1 tablespoon water
          \item 1 cup fresh breadcrumbs
        \end{itemize}
    \end{itemize}
  \end{minipage}
}

\sbox{\method}{%
  \begin{minipage}[t]{0.55\textwidth}
    {\sffamily\bfseries Method}\vspace{0.5ex}
    \begin{enumerate}
      \item Place steamer basket in a medium pot and add enough water to come just below the basket.
        Bring water to a boil. Place potatoes in the steamer basket and cover pot with lid. Steam
        potatoes for 35-40 minutes or until a knife inserted into the center comes out easily.
      \item While potatoes are cooking, whisk together sour cream, egg, cheese, bacon, chives, salt
        and pepper in a large bowl.
      \item Allow potatoes to cool slightly then carefully remove peels. Use a potato ricer to rice
        into a medium bowl.
      \item Add potatoes to sour cream mixture and stir to combine. Taste and adjust seasoning.
      \item Divide potato mixture into 30 portions, about 2 tablespoons each. Roll each portion into
        a ball.
      \item Scramble egg and water in a medium bowl. Place breadcrumbs in a second medium bowl.
      \item Working in batches, roll the balls in the egg. Allow excess egg to drain off then dredge
        balls in breadcrumbs, ensuring they are completely coated.
      \item Arrange balls in a single layer on the airfry basket, leaving space between each piece.
      \item Select AIRFRY/375°F/CONVECTION/20 minutes and press START to preheat oven.
      \item Cook in rack position 4 until brown and crispy, about 20 minutes.
      \item Serve immediately with sour cream for dipping.
    \end{enumerate}
  \end{minipage}
}

\myRecipe{Appetizers}{\mytitle{}}

% \addcontentsline{toc}{subsubsection}{\mytitle}
%   \subsubsection*{\mytitle}
  \begin{tabular}{l}
    \usebox{\ingredients}\quad\usebox{\method}\vspace{3ex}\\
    \multicolumn{1}{c}{\small\ttfamily \url{\myurl}} \\
  \end{tabular}
\end{document}
