% vim: ft=tex:
\documentclass[web-recipes.tex]{subfiles}
\begin{document}

\renewcommand{\mytitle}{Corn and Black Bean Quesadillas (Food Network)}
\renewcommand{\myurl}{https://www.foodnetwork.com/recipes/corn-and-black-bean-quesadillas-3415288}

\sbox{\ingredients}{%
  \begin{minipage}[t]{0.32\textwidth}
    {\sffamily\bfseries Ingredients}\vspace{0.5ex}
    \begin{itemize}
      \item Freshly ground black pepper
      \item Handful of fresh cilantro, chopped
      \item Eight 8-inch round flour tortillas
      \item 8 ounces Monterey Jack cheese, shredded
      \item Pico de gallo, to serve, optional
      \item \nicefrac{1}{4} teaspoon cumin
      \item 1 to 2 tablespoons olive oil
      \item 1 medium onion, chopped
      \item 1 clove garlic, chopped fine
      \item One 15-ounce can black beans, drained and rinsed
      \item 1 cup cooked corn kernels (from 1 large ear)
      \item \nicefrac{3}{4} teaspoon salt
    \end{itemize}
  \end{minipage}
}

\sbox{\method}{%
  \begin{minipage}[t]{0.55\textwidth}
    {\sffamily\bfseries Method}\vspace{0.5ex}
    \begin{enumerate}
      \item Heat 1 tablespoon of oil in a 10-inch nonstick skillet. Add the onion and garlic; cook until lightly golden, 1 to 2 minutes. Add the beans, corn and another tablespoon of oil if the pan seems dry. Season with the salt, cumin and pepper, and stir in the cilantro. Let cook over medium-low heat until the beans and corn are heated through, about 5 minutes.
      \item Heat a 10-inch cast-iron skillet over medium heat.
      \item Meanwhile, arrange the tortillas flat on a counter. Sprinkle 1 \nicefrac{1}{2} tablespoons of cheese on one half of each tortilla. Spoon 2 tablespoons of the bean-corn mixture over the cheese. Top with another 1 1/2 tablespoons of cheese. Fold the filled tortillas into half-moons.
      \item Place 2 quesadillas in the skillet. Cook until golden on the bottom and the cheese has started to melt, 2 to 3 minutes. Use a spatula to flip the quesadillas, and cook until golden on the other side, 2 to 3 more minutes,. Repeat with the remaining quesadillas.
      \item Serve topped with pico de gallo if desired.
      \item Easy Swap In: We usually make the filling with leftover grilled or roasted corn, but frozen corn works great too. Don't thaw the corn-just add the frozen kernels to the pan with the black beans and allow 1 to 2 extra minutes for them to heat through.
    \end{enumerate}
  \end{minipage}
}

\myRecipe{Sandwiches}{\mytitle{}}

% \addcontentsline{toc}{subsubsection}{\mytitle}
%   \subsubsection*{\mytitle}
  \begin{tabular}{l}
    \usebox{\ingredients}\quad\usebox{\method}\vspace{3ex}\\
    \multicolumn{1}{c}{\small\ttfamily \url{\myurl}} \\
  \end{tabular}
\end{document}
