\documentclass[../book.tex]{subfiles}
\begin{document}

\hypersetup{
  pdfauthor = {Food Thinkers},
  pdftitle = {Caramel Apple Turnovers},
}

\section{Caramel Apple Turnovers}
% {\LARGE\bfseries Caramel Apple Turnovers}\vspace{1ex}

{\sffamily Yields 8 turnovers}\vspace{1ex}

	\begin{minipage}[t]{0.35\textwidth}
		{\bfseries\large Ingredients}
    \begin{mydesc}
      \item[For filling]\hfill
        \begin{mying}
        \item 2 medium Granny Smith apples, peeled and diced (about 3 cups)
        \item 3 tablespoons unsalted butter
        \item \nicefrac{1}{2} cup dark brown sugar
        \item 1 teaspoon vanilla extract
        \item 1 teaspoon lemon juice
        \item \nicefrac{3}{4} teaspoon ground cinnamon
        \item \nicefrac{1}{4} teaspoon kosher salt
        \end{mying}
      \item[For turnovers]\hfill
        \begin{mying}
        \item 2 sheets frozen puff pastry (17 ounce package), thawed (keep cold until use)
        \item 1 egg
        \item 1 tablespoon water
        \item Turbinado sugar for sprinkling
        \end{mying}
      \end{mydesc}
      \vspace{1ex}
	\end{minipage}
\quad
  \begin{minipage}[t]{0.6\textwidth}
    {\bfseries\large Instructions}
    \begin{myMethod}
      \item Combine filling ingredients in a medium saucepan and cook over medium heat, stirring occasionally, until apples are tender and syrup is thick, about 10 minutes.
      \item Transfer apple mixture to a plate and chill in the refrigerator until cool to the touch, 20-30 minutes.
      \item Scramble egg and water in a small bowl.
      \item Place 1 sheet of puff pastry on a clean cutting board; reserve second sheet in the refrigerator.
      \item Divide pastry into 4 equal squares. Spoon 2 tablespoons apple mixture onto the center of each square.
      \item Brush the edges of each square with egg wash. Fold pastry diagonally over apple mixture and seal the edges with a fork.
      \item Place turnovers on a plate and refrigerate while preparing remaining turnovers. Repeat steps 4-6 with second sheet of puff pastry.
      \item Select AIRFRY/325°F/SUPER CONVECTION/20 minutes and press START to preheat oven.
      \item Place turnovers on airfry rack. Brush tops with egg wash and sprinkle with turbinado sugar. Make 3 small slits in each turnover.
      \item Cook in rack position 4 until puffed and golden brown, about 20 minutes. Serve warm or at room temperature.
      \end{myMethod}
      \vspace{2mm}
    \end{minipage}
\vfill
\centering\url{https://www.foodthinkers.com/caramel-apple-turnovers/}
\end{document}
