\documentclass[../book.tex]{subfiles}
\begin{document}
\renewcommand{\myTitle}{Oma's Authentic Beef Rouladen}
\renewcommand{\myAuthor}{Quick German Recipes}
\renewcommand{\myURL}{https://www.quick-german-recipes.com/beef-rouladen-recipe.html}
\renewcommand{\myServings}{6 Servings}

\hypersetup{
  pdfauthor = {\myAuthor},
  pdftitle = {\myTitle},
  }

  \section{\myTitle}

  {\small\myServings}\vspace{1ex}

  \begin{minipage}[t]{0.35\textwidth}
    {\large\bfseries Ingredients}
    \begin{mying}
    \item 6 slices top round (see hints below)
    \item salt and freshly ground black pepper, to taste
    \item regular or Dijon mustard, to taste
    \item 3 slices lean bacon, cut into pieces
    \item 3 garlic dill pickles, sliced
    \item 1 onion, sliced
    \item 2 tablespoons butter
    \item 1 - 2 cups water
    \item 1 - 2 tablespoons cornstarch
    \end{mying}
  \end{minipage}
  \quad
  \begin{minipage}[t]{0.6\textwidth}
    {\large\bfseries Instructions}
    \begin{myMethod}
    \item Season the thin slices of beef with salt and freshly ground pepper. Thinly spread
      mustard on top of each slice.
    \item Divide pieces of bacon, dill pickle slices, and onion slices on one end of each of the
      beef slices.
    \item Roll up slices, tucking the ends in and securing each roll with a skewer, wooden
      cocktail stick, or string.
    \item Heat butter in a large skillet over medium heat. Brown beef rolls well on all sides. Do
      not crowd rouladen in skillet, or they will not brown nicely. Do in small batches if
      necessary. Add extra butter if needed.
    \item Once all rouladen are well browned, add 1 to 2 cups of hot water, gently stirring up
      browned bits. Place beef rolls, along with any accumulated juices back in the skillet, bring
      to simmer, and cover.
    \item Simmer for about 1\nicefrac{1}{2} hours.
    \item Remove beef roulades. To thicken gravy, make a cornstarch slurry: combine cornstarch in
      a little cold water and stir gently into cooking liquid until slightly thickened.
    \item Season gravy to taste with salt and freshly ground pepper. If you wish, add sour cream
      for a nice rich gravy.
    \item Remove strings, wooden picks, or skewers from rouladen.
    \item Ladle gravy over the tender beef rolls to serve.
    \end{myMethod}
  \end{minipage}
  \vspace{1ex}
  {\large\bfseries Notes}
  \begin{mying}
  \item Have your local butcher cut beef top round steak (or flank steak) into
    thin slices, about \nicefrac{3}{8}-inch thick. Each roulade should measure at
    least 6 inches by 4 inches. Gently pound meat until it is about
    \nicefrac{1}{8} to \nicefrac{1}{4}-inch thick. Be careful not to put holes in
    the meat. The larger the roulade, the easier it is to roll up.
  \item Some add pickles, others don't. Some add vegetables, others minimize the
    fillings. Use Black Forest ham instead of bacon. Use spicy brown mustard for
    a little heat.
  \item You can use beef broth or beef stock instead of water.
  \item If you're wanting to use your crock pot, in step 5 put everything into
    the slow cooker and cook on high 3-4 hours or low 6-8 hours.
  \end{mying}
  \vfill
  \centering\url{\myURL}
\end{document}
