% vim: ft=tex:
\documentclass[../cookbook]{subfiles}
\begin{document}

\pagestyle{empty}

\renewcommand{\mytitle}{Garlic Naan (A Couple Cooks)}
\renewcommand{\myurl}{https://www.acouplecooks.com/easy-garlic-naan/}

\myRecipe{Breads!naan}{\mytitle{}}

\sbox{\ingredients}{%
  \begin{minipage}[t]{\the\dimexpr 0.35\linewidth - 1em\relax}
    {\sffamily\bfseries Ingredients}\vspace{0.5ex}
    \begin{itemize}
      \item 2 \nicefrac{1}{2} cups (312 grams) all purpose flour
      \item \nicefrac{1}{2} teaspoon baking powder
      \item \nicefrac{1}{4} teaspoon baking soda
      \item 1 \nicefrac{1}{4} teaspoons kosher salt (1 \nicefrac{1}{2} teaspoons, for vegan)
      \item 2 tablespoons olive oil
      \item \nicefrac{3}{4} cup 2\% milk (water, for vegan)
      \item 3 tablespoons Greek yogurt (coconut cream, for vegan)
      \item 2 tablespoons salted butter (coconut oil, for vegan)
      \item 1 garlic clove
      \item Chopped fresh cilantro, for serving
    \end{itemize}
  \end{minipage}
}

\sbox{\method}{%
  \begin{minipage}[t]{\the\dimexpr 0.6\linewidth - 1em\relax}
    {\sffamily\bfseries Method}\vspace{0.5ex}
    \begin{enumerate}
      \item In a large bowl, stir together the all purpose flour, baking powder, baking soda and
        kosher salt. Add the olive oil, milk, and Greek yogurt and stir until dough comes together.
        If it is dry, add a bit more milk; if it is very sticky, add a sprinkle more flour. Knead
        for about 30 seconds to a minute until all the flour is incorporated and a dough ball forms.
      \item Transfer the dough to a lightly oiled bowl. Rest for 30 minutes at room temperature
        covered with a towel.
      \item Once the dough has rested, flatten it into a disc. Then cut it into 6 equal pieces. On a
        clean, lightly floured countertop, roll each dough into a thin teardrop shape, about
        \nicefrac{1}{8}-inch
        thick.
      \item Meanwhile, grate the garlic. In a small saucepan, heat the butter and the garlic over
        medium low heat. Cook for 1 to 2 minutes until the garlic fragrant is just starting to turn
        yellow (but not brown), then immediately remove from the heat.
      \item Heat a cast iron skillet*, griddle or large skillet over very high heat until it’s
        blazing hot (make sure it’s as hot as possible, or the first piece won’t cook correctly).
        Add one of the pieces of dough and cook until the top has bubbles and the bottom is golden
        and very dark brown in spots (about 1 minute), then turn and cook another 30 seconds to 1
        minute on the other side. Brush the naan with a bit of the garlic butter on both sides. Wrap
        it with a clean towel. Repeat with the remaining 5 naan, adding each to the towel afterwards
        (this will steam them and keep them warm and supple).
      \item Serve immediately with chopped cilantro. To store, place fully cooled naan in an
        airtight plastic bag and keep at room temperature for up to 3 days, or wrap in foil, place
        in a plastic bag or container and freeze for up to 2 months. Reheat refrigerated or frozen
        naan by wrapping in aluminum foil and baking in a 350°F oven for 15 minutes. For quick fix,
        you can reheat naan in the toaster (you may need to cut it in half to get it to fit).
    \end{enumerate}
  \end{minipage}
}


  \begin{tabular}{l}
    \usebox{\ingredients}\hspace{1em}\usebox{\method}\vspace{3ex}\\
    \multicolumn{1}{c}{\small\ttfamily \url{\myurl}} \\
  \end{tabular}

\end{document}
