% vim: ft=tex:
\documentclass[../cookbook]{subfiles}
\begin{document}

\pagestyle{empty}

\renewcommand{\mytitle}{Classic Club Sandwich (Serious Eats)}
\renewcommand{\myurl}{https://www.seriouseats.com/classic-club-sandwich-recipe}

\myRecipe{Sandwiches}{\mytitle{}}

\sbox{\ingredients}{%
  \begin{minipage}[t]{\the\dimexpr 0.35\linewidth - 1em\relax}
    {\sffamily\bfseries Ingredients}\vspace{0.5ex}
    \begin{itemize}
      \item 6 slices (about \nicefrac{1}{2}-inch thick) white Pullman loaf
      \item 6 tablespoons mayonnaise
      \item 4 large leaves green leaf lettuce
      \item 3 ounces thickly sliced deli turkey
      \item 6 strips thick-cut bacon, cooked until crisp
      \item 1 large beefsteak tomato (about 6 ounces), sliced
      \item Salt and pepper
      \item \textbf{optional}
        \begin{itemize}
          \item 1 tablespoon mustard
        \end{itemize}
    \end{itemize}
  \end{minipage}
}

\sbox{\method}{%
  \begin{minipage}[t]{\the\dimexpr 0.6\linewidth - 1em\relax}
    {\sffamily\bfseries Method}\vspace{0.5ex}
    \begin{enumerate}
      \item Spread both sides of each bread slice with 4 tablespoons mayonnaise. Toast bread in 2
        batches over medium heat, about 5 minutes, turning once halfway through cooking. Transfer to
        cooling rack.
      \item Spread 4 slices of bread with remaining mayonnaise and mustard. To build sandwiches,
        arrange 1 lettuce leaf on 1 piece of mayo-mustard-spread toast. Top with turkey, then toast,
        then lettuce, bacon, and tomatoes. Season tomatoes with salt and pepper. Top with remaining
        slices of bread and secure each with 4 toothpicks. Cut each sandwich in quarters. Serve.
    \end{enumerate}
  \end{minipage}
}


  \begin{tabular}{l}
    \usebox{\ingredients}\hspace{1em}\usebox{\method}\vspace{3ex}\\
    \multicolumn{1}{c}{\small\ttfamily \url{\myurl}} \\
  \end{tabular}

\end{document}
