\documentclass[../cookbook]{subfiles}
% \documentclass{myRecipe}

\begin{document}

\renewcommand{\myAuthor}{The Yummy Muffin}
\renewcommand{\myTitletext}{Horseradish Cheddar Potato Salad}
\renewcommand{\myUrltext}{https://www.theyummymuffin.com/single-post/horseradish-cheddar-potato-salad}
\renewcommand{\myServingstext}{4}
\renewcommand{\mycourse}{Salads}

\hypersetup{
  pdftitle = {\myTitletext},
  pdfauthor = {\myAuthor}
}

\sbox{\Ingredients}{%
  \begin{minipage}[t]{\the\dimexpr 0.4\textwidth - 2em}
    \par\mySubtitle{Ingredients}
    \par\begin{itemize}
      \item 2 stalks celery, diced
      \item 1 medium shallot, diced
      \item 2 lbs Yukon gold potatoes, diced into \nicefrac{1}{2} inc cubes
      \item 1 tbsp + \nicefrac{1}{4} tsp + \nicefrac{1}{8} tsp salt, divided
      \item \nicefrac{1}{3} cup mayonnaise
      \item 2 tbsp sour cream
      \item 2 tbsp prepared horseradish
      \item \nicefrac{1}{2} tbsp stone ground mustard
      \item \nicefrac{1}{8} tsp pepper
      \item 2 tbsp chives, minced
      \item 1 cup shredded sharp cheddar
    \end{itemize}
  \end{minipage}
}

\sbox{\Instructions}{%
  \begin{minipage}[t]{\the\dimexpr 0.6\textwidth - 2em}
    \par\mySubtitle{Instructions}
    \par\begin{enumerate}
      \item Add celery and shallots to the bottom of a large mixing bowl. Set
        aside.
      \item Prepare the potatoes: Add potatoes to a large pot. Cover with cold
        water until the water reaches about an inch above the potatoes. Add 1
        tbsp salt, and bring to a boil over high heat. Boil potatoes for 5-6
        minutes until the potatoes are fork tender but not falling apart. Drain
        the potatoes, and add to the bowl with the celery and shallots. Do not
        mix. Allow potatoes to cool for 15-20 mins.
      \item Meanwhile, make the dressing. Add mayo, sour cream, horseradish,
        mustard, \nicefrac{1}{8} tsp salt, and pepper to a small mixing bowl. Mix
        well until fully combined. Set aside.
      \item Finish the potato salad: Once the potatoes have cooled for 15-20
        mins, add the dressing, chives, and cheddar. Gently toss to coat the
        potatoes. Taste for seasoning, add a pinch of salt (I added another
        \nicefrac{1}{4} tsp), if desired, and stir again to completely mix. Chill
        the potato salad for at least 2 hours before serving to allow the
        flavors to blend.  Enjoy!
    \end{enumerate}
  \end{minipage}
}

\framebox{
  \cmdRecipe{recipelist}{\mycourse}{\myTitletext}
  \begin{tabular}{ll}
    \multicolumn{2}{l}{\LARGE\bfseries \myTitletext (\myAuthor)} \\ \addlinespace[1mm]
    \multicolumn{2}{l}{Servings: \myServings{\myServingstext}} \\
  \multicolumn{2}{l}{\myUrl{\myUrltext}{\myTitletext}} \\ \addlinespace[3mm]
  \usebox{\Ingredients} & \usebox{\Instructions} \\ \addlinespace[3mm]
\end{tabular}
}

\end{document}
