% vim: ft=tex:
\documentclass[../web-recipes.tex]{subfiles}
\begin{document}

\pagestyle{empty}

\renewcommand{\mytitle}{Jajangmyeon (Delish)}
\renewcommand{\myurl}{https://www.delish.com/cooking/recipe-ideas/a38234424/jajangmyeon-recipe/}

\myRecipe{Mains!Jajangmyeon}{\mytitle{}}

\sbox{\ingredients}{%
  \begin{minipage}[t]{\the\dimexpr 0.35\linewidth - 1em\relax}
    {\sffamily\bfseries Ingredients}\vspace{0.5ex}
    \begin{itemize}
      \item \nicefrac{1}{2} cups vegetable oil
      \item \nicefrac{1}{2} cups Korean black bean paste (chunjang)
      \item \nicefrac{1}{2} lb pork belly, cut into \nicefrac{1}{2}-inch inch cubes
      \item Kosher salt
      \item \nicefrac{1}{2} medium onion, chopped
      \item 1 small zucchini, chopped
      \item 4 cloves garlic, minced
      \item 1 inch piece ginger, minced
      \item 1 \nicefrac{3}{4} cup plus 2 tablespoons water, divided
      \item 1 \nicefrac{3}{4} lb. fresh Korean noodles, or \nicefrac{3}{4} lb dried, long pasta
      \item 1 tablespoon cornstarch
      \item Pinch granulated sugar
      \item Cucumber, cut into matchsticks for garnish
    \end{itemize}
  \end{minipage}
}

\sbox{\method}{%
  \begin{minipage}[t]{\the\dimexpr 0.6\linewidth - 1em\relax}
    {\sffamily\bfseries Method}\vspace{0.5ex}
    \begin{enumerate}
      \item In a small pot over medium heat, add oil and heat until shimmering. Add black bean paste
        and cook, stirring constantly to avoid sticking or burning, until the black bean paste has
        stiffened slightly in texture and is very fragrant, 5 to 7 minutes.
      \item Transfer black bean paste to a bowl, and reserve the remaining oil for cooking.
      \item In a large wok or heavy bottomed pot, heat 2 tablespoons of oil over high heat until it
        shimmers. Season pork belly with salt, then add to the wok. Cook, stirring occasionally,
        until the pork has browned, turned slightly crispy, and some of the fat has rendered, 6 to 8
        minutes.
      \item Add onions and zucchini, and cook until just semi-translucent, 2 to 3 minutes. Add
        garlic and ginger, and cook just until fragrant, about 1 minute. Toss in cabbage and cook
        until wilted, about 2 minutes more.
      \item Stir in the reserved black bean paste. Toss and cook until everything is coated, about 1
        minute. Pour in 1 ¾ cup water, making sure to scrape up any brown bits from the bottom of
        the wok.
      \item Bring mixture to a boil then reduce to a simmer. Cook for about 10 minutes or until the
        sauce is slightly thickened and it coats the back of a spoon. You should be able to draw a
        line through it with your finger.
      \item While the sauce simmers, bring a large pot of water to a boil and add 2 tablespoons of
        salt. Add the noodles and cook according to instructions until just al dente. Drain and
        rinse with cold water.
      \item In a small bowl, combine cornstarch and 2 tablespoons of warm water to make a slurry.
        Add slurry to black bean sauce mixture and stir in fully. Cook until the sauce has reached
        your desired thickness, about 1 to 3 minutes.
      \item To serve, fill bowls with noodles then top with a few ladles of sauce. Top with cucumber
        and serve.
    \end{enumerate}
  \end{minipage}
}


  \begin{tabular}{l}
    \usebox{\ingredients}\hspace{1em}\usebox{\method}\vspace{3ex}\\
    \multicolumn{1}{c}{\small\ttfamily \url{\myurl}} \\
  \end{tabular}

\end{document}
