% vim: ft=tex:
\documentclass[../web-recipes.tex]{subfiles}
\begin{document}

\pagestyle{empty}

\renewcommand{\mytitle}{Classic Club Sandwich (Food Network)}
\renewcommand{\myurl}{https://www.foodnetwork.com/recipes/food-network-kitchen/classic-club-sandwich-recipe-2117730}

\myRecipe{Sandwiches}{\mytitle{}}

\sbox{\ingredients}{%
  \begin{minipage}[t]{\the\dimexpr 0.35\linewidth - 1em\relax}
    {\sffamily\bfseries Ingredients}\vspace{0.5ex}
    \begin{itemize}
      \item 12 slices white bread
      \item \nicefrac{3}{4} cup mayonnaise
      \item 8 romaine lettuce leaves
      \item 16 slices vine-ripened tomatoes
      \item Kosher salt and freshly ground black pepper
      \item 16 slices crispy cooked bacon
      \item 16 ounces sliced roasted turkey
      \item 16 frill picks, or plastic cocktail swords
    \end{itemize}
  \end{minipage}
}

\sbox{\method}{%
  \begin{minipage}[t]{\the\dimexpr 0.6\linewidth - 1em\relax}
    {\sffamily\bfseries Method}\vspace{0.5ex}
    \begin{enumerate}
      \item Toast the bread in a toaster, or under a broiler on both sides. Cut the lettuce leaves
        in half crosswise and form into 8 neat stacks.
      \item To make a double-decker club: On a clean work surface, arrange 3 bread slices in a row.
        Spread 1 tablespoon mayonnaise over 1 side of each bread slice. Place a lettuce stack on top
        of the first bread slice, top with 2 tomato slices, and season with salt and pepper, to
        taste. Place 2 slices bacon over the tomatoes (broken to fit neatly if necessary) and top
        with \nicefrac{1}{8} of the turkey (without letting any hang over the sides). Season the turkey with
        salt and pepper, to taste. Repeat with the second bread slice. Carefully place the second
        layered bread slice on top of the first layered bread, turkey side-up. Cover with the third
        bread slice, mayonnaise side-down.
      \item Pin the sandwich's layers together by piercing them with 4 frill picks or cocktail
        swords through the top bread slice, in 4 places in a diamond-like pattern, all the way to
        the bottom bread slice. Repeat entire process with the remaining ingredients to form 3 more
        sandwiches.
      \item Using a serrated knife cut each sandwich, diagonally, into 4 triangular pieces (each
        piece should be secured in the center with a pick or sword). Serve with potato chips and
        pickles.
    \end{enumerate}
  \end{minipage}
}


  \begin{tabular}{l}
    \usebox{\ingredients}\hspace{1em}\usebox{\method}\vspace{3ex}\\
    \multicolumn{1}{c}{\small\ttfamily \url{\myurl}} \\
  \end{tabular}

\end{document}
