% vim: ft=tex:
\documentclass[../web-recipes.tex]{subfiles}
\begin{document}

\pagestyle{empty}

\renewcommand{\mytitle}{Oma's Authentic Beef Rouladen (Quick German Recipes)}
\renewcommand{\myurl}{https://www.quick-german-recipes.com/beef-rouladen-recipe.html}

\sbox{\ingredients}{%
  \begin{minipage}[t]{0.32\textwidth}
    {\sffamily\bfseries Ingredients}\vspace{0.5ex}
    \begin{itemize}
      \item 6 slices top round (see hints below)
      \item salt and freshly ground black pepper, to taste
      \item regular or Dijon mustard, to taste
      \item 3 slices lean bacon, cut into pieces
      \item 3 garlic dill pickles, sliced
      \item 1 onion, sliced
      \item 2 tablespoons butter
      \item 1 - 2 cups water
      \item 1 - 2 tablespoons cornstarch
    \end{itemize}
  \end{minipage}
}

\sbox{\method}{%
  \begin{minipage}[t]{0.55\textwidth}
    {\sffamily\bfseries Method}\vspace{0.5ex}
    \begin{enumerate}
      \item Season the thin slices of beef with salt and freshly ground pepper. Thinly spread
        mustard on top of each slice.
      \item Divide pieces of bacon, dill pickle slices, and onion slices on one end of each of the
        beef slices.
      \item Roll up slices, tucking the ends in and securing each roll with a skewer, wooden
        cocktail stick, or string.
      \item Heat butter in a large skillet over medium heat. Brown beef rolls well on all sides. Do
        not crowd rouladen in skillet, or they will not brown nicely. Do in small batches if
        necessary. Add extra butter if needed.
      \item Once all rouladen are well browned, add 1 to 2 cups of hot water, gently stirring up
        browned bits. Place beef rolls, along with any accumulated juices back in the skillet, bring
        to simmer, and cover.
      \item Simmer for about 1\nicefrac{1}{2} hours.
      \item Remove beef roulades. To thicken gravy, make a cornstarch slurry: combine cornstarch in
        a little cold water and stir gently into cooking liquid until slightly thickened.
      \item Season gravy to taste with salt and freshly ground pepper. If you wish, add sour cream
        for a nice rich gravy.
      \item Remove strings, wooden picks, or skewers from rouladen.
      \item Ladle gravy over the tender beef rolls to serve.
    \end{enumerate}
  \end{minipage}
}

\myRecipe{Mains!Rouladen}{\mytitle{}}

% \textbf{\Large \mytitle{}}
% \mainlist{main}{\mytitle}
% \addcontentsline{toc}{subsubsection}{\mytitle}

  \begin{tabular}{l}
    \usebox{\ingredients}\quad\usebox{\method}\vspace{3ex}\\
    \multicolumn{1}{c}{\small\ttfamily \url{\myurl}} \\
  \end{tabular}
\end{document}
