\documentclass[../web-recipes.tex]{subfiles}
\begin{document}

\renewcommand{\myAuthor}{theKitchn}
\renewcommand{\myTitletext}{Farmer's Lunch Sandwich}
\renewcommand{\myUrltext}{https://www.thekitchn.com/recipe-farmers-lunch-sandwich-85363}
\renewcommand{\myServingstext}{4 sandwiches}
\renewcommand{\mycourse}{Sandwiches}

\hypersetup{
  pdftitle = {\myTitletext},
  pdfauthor = {\myAuthor}
}

\sbox{\Ingredients}{%
  \begin{minipage}[t]{\the\dimexpr 0.4\textwidth - 2em}
    \par\mySubtitle{Ingredients}
    \par\begin{itemize}
      \item 1 loaf crusty baguette or ciabatta
      \item Whole grain mustard
      \item Sharp cheddar cheese
      \item Butter lettuce
      \item 2 hard, tart apples like Granny smith or Braeburn, very thinly sliced
      \item 2 to 3 tablespoons lemon juice (from one lemon)
      \item Onion-Thyme Jam
    \end{itemize}
  \end{minipage}
}

\sbox{\Instructions}{%
  \begin{minipage}[t]{\the\dimexpr 0.6\textwidth - 2em}
    \par\mySubtitle{Instructions}
    \par\begin{enumerate}
      \item Slice the baguette into four sections and slice the sections in half
        length-wise. Spread a little whole grain mustard on both halves.
      \item Smear a layer of onion jam on the bottom half. Toss the apple slices in a
        little lemon juice, and then add them to the sandwich. Add a few leaves of lettuce
        and then top with a layer of cheese. Press the sandwich closed.
      \item If not eating right away, wrap the sandwiches in a tight layer of wax paper.
        Keep them in a cool place — like a picnic hamper! — until you're ready to eat
        them. They'll be ok left unrefrigerated for several hours.
    \end{enumerate}
  \end{minipage}
}

\begin{tabular}{ll}
  \multicolumn{2}{l}{\myTitle{\mycourse}{\myTitletext (\myAuthor)}}\\ \addlinespace[1mm]
	\multicolumn{2}{l}{\myServings{\myServingstext}} \\
  \multicolumn{2}{l}{\myUrl{\myUrltext}{\myTitletext}} \\ \addlinespace[3mm]
  \usebox{\Ingredients} & \usebox{\Instructions} \\ \addlinespace[3mm]
\end{tabular}

\end{document}
