\begin{description}
  \item[Chicken Strips]\hfill
    \begin{enumerate}
    \item Cut chicken into strips about 1-inch wide. In a medium bowl,
      toss chicken with \nicefrac{1}{2} teaspoon salt. Cover and refrigerate while
      preparing breading.
    \item Combine spices in a small bowl and mix well. Reserve.
    \item Combine \nicefrac{1}{2} cup panko, \nicefrac{3}{4} teaspoon salt and 1 tablespoon spice
      mix in the bowl of a food processor. Pulse until finely ground,
      about 10 pulses. Transfer panko mixture to a shallow dish and add
      olive oil and remaining 1 cup panko. Use fingers to mix, ensuring
      olive oil is evenly distributed.
    \item Place flour in a second shallow dish and stir in remaining spice mix.
    \item Scramble the egg and 1 tablespoon water in a third shallow dish.
    \item Working in batches, toss chicken strips in flour and shake off any excess. Dip chicken in egg and allow excess to drain off. Dredge chicken in panko mixture, ensuring all sides are well crusted.
    \item Arrange chicken strips in a single layer on the airfry basket, leaving space between each piece.
    \item Select AIRFRY/425°F/SUPER CONVECTION/8 minutes and press START to preheat oven.
    \item Cook in rack position 4 until crisp, about 8 minutes.
    \item Serve immediately with honey mustard sauce.
    \end{enumerate}
  \item[Honey Mustard Sauce]\hfill
    \begin{enumerate}
    \item Combine all ingredients in a small bowl and stir until well combined. Cover and chill until ready to use.
    \end{enumerate}
  \end{description}

